CVS Installation und Konfiguration

### 2013-06-18 CM-Scripts/studentuserlist.tex
Maintenance of files and cvs-Documentation for change from simone to fabio.
Thomas Alber added

@@

\begin{longtable}{|l|l|l|l|l|l|l|l|}

@@

\textbf{Linux-User}        &\textbf{CVS-User}        &\textbf{Student}&\textbf{E-Mail}   &\textbf{Verzeichnis}            &\textbf{von}&\textbf{bis}\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand1 &rentergent&Lisa Rentergent &lisa@rentergent.de&Javagui/viewer/queryconstruction&16.4.12     &\\

@@

\cellcolor{green}           &uchdorf                  &Thomas Uchdorf  &                  &Algebras/OSM                    &8.2.11      &5.3.12\\
\cellcolor{green}           &vjohn                    &Volker John     &                  &Algebras/OptAux                 &            &8.2.11\\
\rowcolor{yellow}\cellcolor{green}diplomand2 & keberl    &Katharina Rieder&keberl@web.de&Algebras/TrajetoryAnnotation                       &16.4.12     &\\
\cellcolor{green}           &fpanse                   &Frank Panse     &                  &Algebras/SymbolicTrajectory     &21.12.10    &5.3.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand3   & eckebre   &Jens Eckebrecht &jens@eckebrecht.de&Algebras/RobustPlaneSweep       &21.12.12    & \\

@@

\cellcolor{red}             &kubusch                  &Rico Kubusch    &rico.kubusch@bka.bund.de&                          &21.6.11     &21.12.12\\

@@

\cellcolor{red}             &bponeleit                &Burkhard Poneleit&                  &Optimizer/Subqueries           &            &8.2.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand4   & walther   &Daniel Walther  &Da.walther@gmx.de &Tools/SecondoPostGIS            &22.2.13     &\\

@@

\cellcolor{red}             &kkoch                    &Katja Koch      &katjakoch1@googlemail.com&Algebras/RobusGeometry   &2.1.12      &21.12.12\\

@@

\cellcolor{red}             &geduldig                 &Jochen Geduldig &                   &Algebras/NestedRelation2       &8.9.10      &2.1.12\\

@@

\cellcolor{red}             &kteufel                  &Klaus Teufel    &                   &Algebras/NestedRelation        &            &8.9.10\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   & zacher    &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&Algebras/Tile      &18.4.13     &\cellcolor{red}Laptop\\

@@

\cellcolor{red}             &tachmann                 &Thomas Achmann  &t\_achmann@gmx.de  &Algebras/Distributed           &16.2.11     &21.12.12\\

@@

\cellcolor{red}             & totim     &Tobias Timmerscheidt&               &Algebras/DistributedRelation   &15.1.10     &16.2.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand6   & floheinz &Florian Heinz    &fh@sysv.de         &Algebras/RegionInterpolation2 und Javagui/viewer/v3d &26.4.13 &\\

@@

\cellcolor{red}             &srenner                 &Stefanie Renner  &stefanie.renner@gmx.de&Algebras/MovingRegion2      &9.11.11     &21.12.12\\

@@

\cellcolor{red}             &sjung                   &Sven Jungnickel  &                   &Algebras/ExtRelation2          &            &8.2.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand7   & steigerk &Kristina Steiger  &tinasteiger@gmx.net&WebGui                         &6.5.13      &\\

@@

\cellcolor{red}             &geisbues                &Simon Geisbuesch  &simon.geisbuesch@o2online.de&Algebras/SpatialJoin2 &14.11.11    &21.12.12\\

@@

\cellcolor{red}             &zdahmen                 &Zoryana Dahmen-Lobur&                 &/DahmenLobur                  &20.10.10    &8.2.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand8   & kuepper   &Michael K\"upper  &kuepper.michael@gmail.com&AndroidGui              &6.5.13      &\\

@@

\cellcolor{red}             &linsenme                 &Linsenmeier       &                   &Algebras/SpatialJoin und Algebras/NearestNeighbour& &8.2.11\\

@@

\cellcolor{green}diplomand9 &mroth                    &Matthias Roth     &Fernstudium@planet-roth.de&Algebras/MapMatching   &21.11.11    &21.12.12\\

@@

\cellcolor{green}           &whoffmann                &Walter Hoffmann   &                    &secondo\_Whoff               &1.2.10      &8.2.11\\

@@

\cellcolor{green}           &herkert                  &A.Herkert         &                   &LargeQueries                  &1.3.10       &8.2.11\\

@@

\cellcolor{green}           &danbro                   &Daniel Brockmann  &                   &Algebras/UGrid                &14.4.10       &8.2.11\\

@@

\cellcolor{green}diplomand12&mtirtasana               &Matthias Tirtasana&matthias.tirtasana@science-computing.de&OptParser &5.3.12       &21.12.12\\

@@

\cellcolor{green}           &wrede                    &Nina Wrede        &                    &Algebras/Network2 und Algebras/TemporalNet2&15.6.10&2.1.12\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand13& nidzwetzki&Jan Nidzwetzki    &nidzwetzki@gmx.de   &Algebras/CostEstimation        &18.4.12   &\\

@@

\cellcolor{green}diplomand14&flehmann                 &Frank Lehmann     &fraleco@gmx.de      &Algebras/SymbolicTrajectory2   &23.4.12   &12.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand15  & nvkempen                 &Nicolai van Kempen&nikolaivank@googlemail.com&Optimizer/NestedRelations Optimizer/MemoryAllocation&24.4.12&\\

@@

\cellcolor{green}diplomand16&jmoeller                  &Jasmin Moeller    &JasminMoeller@gmx.de &Algebras/Cluster2      &28.6.12  &21.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand17 &ofeuer                     &Oliver Feuer      &ofeuer\_informatik@yahoo.de&Algebras/Region2 und MovingRegion3&11.10.12&\cellcolor{red}Laptop\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand18&sfuhs                       &Svenja Fuhs        &svenja.fuhs@t-online.de  &Algebras/Precise2D       &29.10.12&\\

@@

\end{longtable}

>>>>

\usepackage{tabu}

@@

\begin{longtabu}to 1\textwidth{|l|l|l|l|l|X|l|l|}

@@

\textbf{Linux-User}        &\textbf{CVS-User}        &\textbf{Student}&\textbf{E-Mail}       &\textbf{Verzeichnis}              &\textbf{von} &\textbf{bis}\\
\hline\endhead
\rowcolor{yellow}\cellcolor{green}diplomand1 &alber  &Thomas Alber    &th.alber@loop.de      &Javagui/viewer/queryconstruction2 &17.06.13     &\\
\cellcolor{red}            &rentergent               &Lisa Rentergent &lisa@rentergent.de    &Javagui/viewer/queryconstruction  &16.04.12     &17.06.13\\
\cellcolor{red}            &uchdorf                  &Thomas Uchdorf  &                      &Algebras/OSM                      &08.02.11     &05.03.12\\
\cellcolor{red}            &vjohn                    &Volker John     &                      &Algebras/OptAux                   &             &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand2 &keberl &Katharina Rieder&keberl@web.de         &Algebras/TrajetoryAnnotation      &16.04.12     &\\

@@

\cellcolor{green}          &fpanse                   &Frank Panse     &                      &Algebras/SymbolicTrajectory       &21.12.10     &05.03.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand3   &eckebre&Jens Eckebrecht &jens@eckebrecht.de    &Algebras/RobustPlaneSweep         &21.12.12     & \\

@@

\cellcolor{red}            &kubusch                  &Rico Kubusch    &rico.kubusch@bka.bund.de&                                &21.06.11     &21.12.12\\

@@

\cellcolor{red}            &bponeleit                &Burkhard Poneleit&                     &Optimizer/Subqueries              &             &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand4   &walther&Daniel Walther  &da.walther@gmx.de     &Tools/SecondoPostGIS              &22.02.13     &\\

@@

\cellcolor{red}            &kkoch                    &Katja Koch      &katjakoch1@googlemail.com&Algebras/RobustGeometry        &02.01.12     &21.12.12\\

@@

\cellcolor{red}            &geduldig                 &Jochen Geduldig &                      &Algebras/NestedRelation2          &08.09.10     &02.01.12\\

@@

\cellcolor{red}            &kteufel                  &Klaus Teufel    &                      &Algebras/NestedRelation           &             &08.09.10\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand5   &zacher &Dirk Zacher     &dirk.zacher@fernuni-hagen.de&Algebras/Tile               &18.04.13     &\cellcolor{red}Laptop\\

@@

\cellcolor{red}            &tachmann                 &Thomas Achmann  &t\_achmann@gmx.de     &Algebras/Distributed              &16.02.11     &21.12.12\\

@@

\cellcolor{red}            &totim                    &Tobias Timmerscheidt&                  &Algebras/DistributedRelation      &15.01.10     &16.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand6   &floheinz&Florian Heinz  &fh@sysv.de            &Algebras/RegionInterpolation2 \& Javagui/viewer/v3d &26.04.13 &\\

@@

\cellcolor{red}            &srenner                  &Stefanie Renner &stefanie.renner@gmx.de&Algebras/MovingRegion2            &09.11.11     &21.12.12\\

@@

\cellcolor{red}            &sjung                    &Sven Jungnickel &                      &Algebras/ExtRelation2             &             &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand7   &steigerk&Kristina Steiger&tinasteiger@gmx.net  &WebGui                            &06.05.13     &\\

@@

\cellcolor{red}            &geisbues                 &Simon Geisbuesch&simon.geisbuesch@o2online.de&Algebras/SpatialJoin2       &14.11.11     &21.12.12\\

@@

\cellcolor{red}            &zdahmen                  &Zoryana Dahmen-Lobur&                  &/DahmenLobur                      &20.10.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand8   &kuepper&Michael K\"upper&kuepper.michael@gmail.com&AndroidGui                     &06.05.13     &\\

@@

\cellcolor{red}            &linsenme                 &Linsenmeier     &                      &Algebras/SpatialJoin \& Algebras/NearestNeighbour& &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand9   &issa   &Hamza Adnan Issa&hamza.adnan.issa@gmail.com&Algebras/HybridTrajectory     &11.06.13     &\\

@@

\cellcolor{red}            &mroth                    &Matthias Roth   &Fernstudium@planet-roth.de&Algebras/MapMatching          &21.11.11     &21.12.12\\
\cellcolor{red}            &whoffmann                &Walter Hoffmann &                      &secondo\_Whoff                    &01.02.10     &08.02.11\\

@@

\cellcolor{green}          &herkert                  &A. Herkert      &                      &LargeQueries                      &01.03.10     &08.02.11\\

@@

\cellcolor{green}          &danbro                   &Daniel Brockmann&                      &Algebras/UGrid                    &14.04.10     &08.02.11\\

@@

\cellcolor{green}diplomand12&mtirtasana              &Matthias Tirtasana&matthias.tirtasana@science-computing.de&OptParser      &05.03.12     &21.12.12\\

@@

\cellcolor{green}          &wrede                    &Nina Wrede      &                      &Algebras/Network2 \& Algebras/TemporalNet2&15.06.10&02.01.12\\

@@

\rowcolor{yellow}\cellcolor{green}diplomand13&nidzwetzki&Jan Nidzwetzki&nidzwetzki@gmx.de    &Algebras/CostEstimation           &18.04.12     &\\

@@

\cellcolor{green}diplomand14&flehmann                &Frank Lehmann   &fraleco@gmx.de        &Algebras/SymbolicTrajectory2      &23.04.12     &12.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand15&nvkempen &Nicolai van Kempen&nikolaivank@googlemail.com&Optimizer/NestedRelations \& Optimizer/MemoryAllocation&24.04.12&\\

@@

\cellcolor{green}diplomand16&jmoeller                &Jasmin Moeller  &JasminMoeller@gmx.de  &Algebras/Cluster2                 &28.06.12     &21.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand17&ofeuer   &Oliver Feuer    &ofeuer\_informatik@yahoo.de&Algebras/Region2 \& MovingRegion3&11.10.12 &\cellcolor{red}Laptop\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand18&sfuhs    &Svenja Fuhs     &svenja.fuhs@t-online.de&Algebras/Precise2D               &29.10.12     &\\

@@

\end{longtabu}
